### 2016-08-23 JSM/VizInfSlides.Rmd
add screen grabs from experiment

## Results 1

``` {r, echo=FALSE}
tab <- readr::read_csv("../Results/turk21_users.csv")
res <- readr::read_csv("../Results/turk21_feedback.csv")
```

- barchart with filled correct

@@

- scatterplot of %correct by beta 3
- scatterplot of %correct by #jtt

@@

- Doesn't work for networks
- Need another way! (layout?)

>>>>

## Results

``` {r, echo=FALSE, fig.align = 'center'}
ids <- readr::read_csv("https://raw.githubusercontent.com/erichare/lineups/f19635a00507210013ba9e631761ad0c89a6564d/experiments/turk21/details/picture-details.csv")
tab <- readr::read_csv("../Results/turk21_users.csv")
res <- readr::read_csv("../Results/turk21_feedback.csv")
res2 <- left_join(res, ids, by = 'pic_id')
res3 <- res2 %>% filter(test_param %in% c("smallfriends", "smallfriends-rev")) 
res3$correct <- res3$response_no == res3$obs_plot_location
ggplot(data = res3) + 
  geom_bar(aes(x = as.factor(response_no), fill = correct)) + 
  facet_wrap(~data_name) + coord_flip() + 
  labs(x = "response", y = "count") + 
  theme(axis.text.y = element_blank())
```

@@

```{r, echo=FALSE}
lus_jtts <- readr::read_csv("../Data/lineups-jtt.csv")
load("../Data/lus_ests_truth.rda")

res4 <-left_join(res3, lus_jtts, by = c("data_name" = "filename", "obs_plot_location" = "plot_order"))
res4.2 <- res4 %>% group_by(data_name, jtt) %>% summarise(perc_corr = sum(correct)/n())
p1 <- ggplot(data = res4.2) +geom_point(aes(x = jtt, y = perc_corr)) + labs(x = "Number of jumping transitive triplets", y = "Percent of Participants Choosing Correctly")
res3a <- res3
res3a$data_name <- sub(".csv", "", res3a$data_name)
res3a$data_name <- sub("-m-", "-", res3a$data_name)
res3a$data_name <- sub("-rep-", "-", res3a$data_name)
exp_names <- unique(res3a$data_name)
lus_truth2 <- lus_ests_truth %>% 
  filter(param_name == "transitive triplets jumping alcohol2" &
           lineupid %in% exp_names & model == "M2")
res5 <- left_join(res3a, lus_truth2, by = c("data_name" = "lineupid",
                                            "obs_plot_location" = "panel_num"))
res5.2 <- res5 %>% group_by(data_name, param_est) %>% 
  summarise(perc_corr = sum(correct)/n())
p2 <- ggplot(data = res5.2) + geom_point(aes(x = param_est, y = perc_corr)) + labs(x = "Parameter estimate", y = "Percent of Participants Choosing Correctly")
gridExtra::grid.arrange(p1, p2, nrow = 1)
```

@@

- Doesn't work for networks
- Need another way (layout?)

### 2016-08-23 Results/TurkExp1WriteUp.Rnw
add screen grabs from experiment

The outdegree and reciprocity effects are the most important effects to any SAOMs. The outdegree effect ``always must be included," and the reciprocity effect ``practically always must be included" {\color{green} (CITE Rsiena Manual, p 41)}. The outdegree of a node in a network is a measure of how active that node is within the network, while the reciprocity parameter measures of how often a node's outgoing ties are reciprocated.  The additional effects, jumping transitive triplets and doubly achieved distance, were deemed very significant by a $t$-test.

@@

In order to become a subject in our experiment, the Amazon turk user had to first read through some introductory material and prove they could identify the correct plot in two test lineups, one for M1 v. M2 and one for M2 v. M1. These two lineups were constructed to be very simple in order to train the turkers. Once the turker made it into the experiment, they looked at 10 lineups selected at random from a pool of 25. There were five lineups for each of the four types with an additional five lineups of the type M1 v. M2 which were chosen for their high counts of jumping transitive triplets in the alternative model network.

\section{Appendix}

>>>>

The outdegree and reciprocity effects are the most important effects to any SAOMs. The outdegree effect ``always must be included," and the reciprocity effect ``practically always must be included" {\color{green} (CITE Rsiena Manual, p 41)}. The outdegree of a node in a network is a measure of how active that node is within the network, while the reciprocity parameter measures of how often a node's outgoing ties are reciprocated.  The additional effects, jumping transitive triplets and doubly achieved distance, were deemed very significant by a $t$-test, which was why we chose them for testing.

@@

In order to become a subject in our experiment, the Amazon turk user had to first read through some introductory material and prove they could identify the correct plot in two test lineups, one for M1 v. M2 and one for M2 v. M1. These two lineups were constructed to be very simple in order to train the turkers. Once the turker made it into the experiment, they looked at 10 lineups selected at random from a pool of 25. There were five lineups for each of the four types with an additional five lineups of the type M1 v. M2 which were chosen for their high counts of jumping transitive triplets in the alternative model network in an attempt to gauge how important this statistic is to the visualization of the network. If there are many jumping transitive triplets in the alternative model plot and more turkers correctly choose that plot, that would be evidence that the jumping transitive triplets are very noticeable to the user. \st{????}

\section{Procedure}

Each Amazon Turk user was greeted with the following message: ``In this survey a series of similar looking charts will be presented. We would like you to respond to the following questions.
\begin{enumerate}
\item Pick the plot based on the survey question
\item Provide reasons for choice
\item How certain are you?
\end{enumerate}
Finally we would like to collect some information about you. (age category, education and gender)."  Then, they were led through a training page about how to identify the correct plot in a lineup, seen in Figure~\ref{fig:lineupex}. Then, they saw two trial plots that they had to get correct in order to proceed to the rest of the experiment. They chose the plot that looked the most different from the others, why they chose is (most complex, least complex, or other), and how certain they were that they had chosen correctly (Very Uncertain, Uncertain, Neutral, Certain, Very Certain). These trial plots are shown in Figure~\ref{fig:lineuptrial}

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 1}
\includegraphics[width=\textwidth]{Ex1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Example 2}
\includegraphics[width=\textwidth]{Ex2}
\end{subfigure}
\caption{\label{fig:lineupex} The first training page in the Amazon Turk experiment.}
\end{figure}

\begin{figure}
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 1}
\includegraphics[width=\textwidth]{Trial1}
\end{subfigure}\hfill
\begin{subfigure}[t]{.45\textwidth}
\caption{Trial 2}
\includegraphics[width=\textwidth]{Trial2}
\end{subfigure}
\caption{\label{fig:lineupex} The trial plots that users had to get correct in order to participate in the Amazon Turk experiment.}
\end{figure}
